Joint training of classification model and similarity model for low-resource text classification in chatbot

### 2020-08-26 chatbot_classification/aaai_2021/paper.tex
modified:   paper.pdf   modified:   paper.tex   modified:   paper.ver_03.pdf

  todo: joint training of intention and NER.

@@

  \begin{figure}[htbp]
    \centering 
    \subfigure[classification model]{
      \label{Fig.1.sub.1}
      \includegraphics[scale=0.7]{picture/picture1.pdf}
    }
    \subfigure[similarity model]{
      \label{Fig.1.sub.2}
      \includegraphics[scale=0.55]{picture/picture2.pdf}
    }
    \caption{Two popular structures of building task-specific conversational chatbot}
    \label{Fig.1.main}
  \end{figure}

@@

  \begin{figure}[htbp]
    \begin{centering}
      \includegraphics[scale=0.48]{picture/picture3}
      \par
    \end{centering}
    \caption{
      \textbf{Network  Structure  of  2-stage SFC:} a joint system of multi-task
      for  both  text  classification task and sentence-pair semantic similarity
      task.
    }
    \label{fig:ver.1.3}
  \end{figure}

@@

  However,  since  the auxiliary tool in joint system mentioned above works in a
  separate  stage  from  sentence-pair model, we find the the quality of sampled
  candidate  classes  might  limit  the  overall  performance  of SFC, since the
  candidate  classes  for  each user query is always fixed during the multi-task
  training  process. This observation motivates us to further improve SFC into a
  joint  model  of  sentence-pair  model  and  text  classification  model  in a
  hierarchical  architecture  by  putting  different  tasks at different network
  layers \cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
  together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
  model  involved in joint training process replace the role of auxiliary tools.
  In  this  way, the sentence pairs selected from top-K classes becomes dynamic,
  which  means  the  text classification model will also be further optimized to
  provide better top-K classes pooling result.

@@

  \begin{figure*}[t]
    \begin{centering}
      \includegraphics[scale=0.72]{picture/picture4} 
      \par
    \end{centering}
    \caption{
      \textbf{Network   Structure   of  hierarchical  SFC:}  a  joint  model  of
      sentence-pair   model   and   text   classification   model  organized  in
      hierarchical  structure by completing different tasks at different network
      layers.
    }
    \label{fig:framework}
  \end{figure*}

  \section{Methodology}
  In  this  section,  we  will  describe a system of similarity model fused with
  classification  model,  named  as  SFC, in detail. We come up with 2 different
  approaches  for  implementation  of SFC system, in which hierarchical SFC is a
  further improvement of 2-stage SFC for better performance.

  \subsection{2-stage SFC with multi-task learning}

  The   detailed   network   structure   of   2-stage   SFC  is  shown  in  Fig.
  \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
  different  jobs. In stage 1, we can use any auxiliary model or tool to provide
  top-K  most  related class labels for sampling sentence pairs of both positive
  samples  and negative samples for stage 2. Suppose we have a training data set
  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
  is the user input query and $y_{i}$ is a single class label from a class label
  set  of  $C$  classes  in total. If we want to generate sentence pair data set
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
  similarity class label, see Equ. \ref{eq:similarity label},
  \begin{align}
    l_{j}=
    \begin{cases} \label{eq:similarity label}
      0 & y_{x}\neq y_{x'}\\
      1 & y_{x}=y_{x'}
    \end{cases}
  \end{align}
  directly  from  original data set $\mathcal{D}$ without any sampling strategy,
  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
  might be too time-consuming for the training process of stage 2 since we often
  have  hundreds  of class labels under task-specific chatbot scenario. Although
  we  may  only  have  a  few data points for a single class label, $M$ is still
  quite a big number.

@@

  After  explaining the data sampling principle for sentence pairs and how the 2
  stages  in  SFC  system  connect  with  each other, let's go deeper into model
  structure within these 2 stages respectively to see how it works.

@@

  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq: 2-stage SFC loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.

  \begin{align}
    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
    \label{eq: 2-stage SFC loss}
  \end{align}

@@

  \subsection{hierarchical SFC with joint model structure}
  Despite  the  outstanding experimental result of 2-stage SFC on various tasks,
  we still find a limitation brought by the 2-stage system structure. In 2-stage
  SFC, Stage 1 and stage 2 are separate, so they do not interact with each other
  during  training.  In  this  case,  the  performance  of stage 1 can limit the
  potential  of  stage  2, meanwhile, stage 2 also cannot give training feedback
  back to stage 1 for fine-tuning.

  Therefore,  to  further  improve the overall performance of SFC, we proposed a
  hierarchical  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
  hierarchical SFC, classification model is being placed in lower layer level to
  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
  similarity  model  placed in higher layer level through a top-K pooling layer.
  In  this way, classification model and similarity model can be merged into one
  single  joint-model  for  multi-task training with sentence pairs sampled from
  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
  separate stage structure.

  There  are  3  tasks in total during the training process of hierarchical SFC,
  shown  in  Fig. \ref{fig:framework}, and the overall loss is also the weighted
  sum  of  all  the task-specific losses, shown in Equ. \ref{eq: hierachical SFC
  loss}. Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1:
  sentence-pair  similarity,  task  2:  top-K classification and task 3: general
  single   sentence  classification  respectively,  which  are  $\alpha_S=0.25$,
  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.

@@

          2-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline

@@

          2-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline

@@

          2-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline

@@

          \multirow{2}*{Hierarchical SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

@@

  \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
  based  on  the network structure of 2-stage SFC shown in \ref{fig:ver.1.3}. We
  conduct  ablation study by introducing single task SFC system with only Task 1
  or  Task  2  to  investigate  the influence of each component within the total
  loss.

@@

      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline 
        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& 2-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7882$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7826$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& 2-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & Hierarchical SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
        \hline
      \end{tabular}
      \par
    \end{centering}
    \caption{
      We  show the performance of SFC from different settings of hyperparameters
      for  $K$,  the candidate class number, and $P$, the sample number for each
      class.
    }

@@

  \textbf{Comparison  among  SFC  variants.} First, we turn to compare among the
  four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
  brought  by  multi-task  and  hierarchical  joint-model  structure. We conduct
  ablation  experiments  to study the benefits brought by multi-task training by
  comparing multi-task 2-stage SFC with single-task 2-stage SFC. We can see from
  Table  \ref{tbe:table2}  that  2-stage  SFC  with  only  task 1 (sentence-pair
  similarity task) degrades by 0.65 percent on average and 2-stage SFC with only
  task  2  (top-K  classification  task) degrades by 0.3 percent on average. The
  degradation  indicates  that  training  with these 2 tasks together in SFC can
  effectively  help  the  sentence-pair  model  extract  more knowledge from the
  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
  1.  This observation suggests that task 2 may play a relatively more important
  role  in multi-task learning, which leads us to put larger weight $\alpha_{K}$
  to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
  $\mathcal{L}$.  Also, we can see that the hierachical SFC steadily outperforms
  2-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
  observation  supports  the idea that the hierachical joint model structure can
  alleviate the limitation brought by the lack of interaction between similarity
  model  and  classification  model in 2-stage SFC. Therefore, for the following
  analysis,  we  will  focus  on  the comparison between hierachical SFC and the
  other baseline models.

  \textbf{Analysis  under  few-shot  scenarios.}  Next,  we  analyze the overall
  improvement trend of SFC under various few-shot settings. Our main focus is to
  study chatbot building in common situation during real-world application where
  only  a  few  sample  sentences are available for each class. The experimental
  results  for  the  3  diverse  intent detection datasets (ClINC150, BANKING77,
  HWU64) under few-shot settings indicate that our proposed hierarchical SFC can
  achieve  2.47  percents  average  improvement  over  one  of the most powerful
  baseline  models,  which  is  RoBERTa-large classification model, on all these
  few-shot  settings. Moreover, the improvement in F-score becomes more and more
  prominent  with the decrease of data sample number per class. Our hierarchical
  SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
  classification model in the most extreme few-shot setting with only 5 training
  samples  per class. This observation indicates that SFC is especially suitable
  for  being  applied during the initial stage of building task-specific chatbot
  system,  where  the  amount  of  data sample for each class label is extremely
  scarce.

  \textbf{Comparison  between  label  embedding  and  sentence  pair embedding.}
  Afterwards,  we  start  to  compare the performance of SFC with the text-label
  joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
  hierarchical  SFC outperforms LEAM by 14.25 percents on average F-score over 5
  datasets.  Besides,  although the labels within the 3 diverse intent detection
  datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
  semantic  summary  of  each intent, hierarchical SFC still outperforms LEAM by
  14.69  percents  on  average  F-score.  This  observation  indicates that it's
  usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
  representative  of  all  the  sentences  within a class since there are always
  plenty of ways for people to express questions or queries about the same topic
  during   a   conversation  with  chatbot.  Therefore,  learning  the  semantic
  similarity  between  user  query  and  sample  sentences through sentence pair
  embedding  can be more reliable than making decision according to the semantic
  relationship between user query and class labels through label embedding.

  \textbf{Fusion  of  classification  and  similarity  model.} Then, we begin to
  compare  the  general  performance  of SFC with single-task classification and
  similarity  baselines.  As  for  the  classification  model,  hierarchical SFC
  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   17.87
  percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
  unstable  for  classification  task.  Here, we did multiple run with different
  settings  of parameters such as learning rate and batch size for each dataset,
  and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
  BERT-large  by  9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by
  2.47 percents on average F-score over 5 datasets. In this way, we can see that
  RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
  classification  task  we  are  studying.  As for the similarity model, we only
  choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
  hierarchical  SFC  achieves  the  improvement  of  7.81  percents  on average.
  Moreover,  hierarchical  SFC's  result on 2 datasets without data sampling for
  few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
  percents  higher  than  Roberta-large  classification  model, and are 6.96 and
  10.77  percents higher than Roberta-large similarity model. These improvements
  illustrate that putting classification model and similarity model at different
  network  layers  to  cooperate  with  each  other  is  a  successful design of
  hierarchical network structure for joint model, which enables these two models
  assist each other for better overall results.

>>>>

@@

@@

@@

  However,  since  the auxiliary tool in joint system mentioned above works in a
  separate  stage  from  sentence-pair model, we find the the quality of sampled
  candidate  classes  might  limit  the  overall  performance  of SFC, since the
  candidate  classes  for  each user query is always fixed during the multi-task
  training  process. This observation motivates us to further improve SFC into a
  joint  model  of  sentence-pair  model  and  text  classification  model  in a
  joint  architecture  by  putting  different  tasks at different network
  layers \cite{sogaard2016deep,   hashimoto2016joint}   and  then  training  them
  together,  shown  in  Fig  \ref{fig:framework}.  Here, the text classification
  model  involved in joint training process replace the role of auxiliary tools.
  In  this  way, the sentence pairs selected from top-K classes becomes dynamic,
  which  means  the  text classification model will also be further optimized to
  provide better top-K classes pooling result.

@@

  \begin{figure*}[t]
    \begin{centering}
      \includegraphics[scale=0.72]{picture/picture4} 
      \par
    \end{centering}
    \caption{
      \textbf{Network   Structure   of  joint  SFC:}  a  joint  model  of
      sentence-pair   model   and   text   classification   model  organized  in
      joint  structure by completing different tasks at different network
      layers.
    }
    \label{fig:framework}
  \end{figure*}

  \section{Methodology}
  In  this  section,  we  will  describe a system of similarity model fused with
  classification  model,  named  as  SFC, in detail. We come up with 2 different
  approaches  for  implementation  of SFC system, in which joint SFC is a
  further improvement of two-stage SFC for better performance.

  \subsection{two-stage SFC with multi-task learning}

  The   detailed   network   structure   of   two-stage   SFC  is  shown  in  Fig.
  \ref{fig:ver.1.3}.  It  is  composed  with  2  separate  stages  in  charge of
  different  jobs. In stage 1, we can use any auxiliary model or tool to provide
  top-K  most  related class labels for sampling sentence pairs of both positive
  samples  and negative samples for stage 2. Suppose we have a training data set
  $\mathcal{D}=\{x_{i},y_{i}\}_{i=1}^{N}$  of  $N$ data points, in which $x_{i}$
  is the user input query and $y_{i}$ is a single class label from a class label
  set  of  $C$  classes  in total. If we want to generate sentence pair data set
  $\mathcal{D'}=\{[(x,x')_{j},l_{j}]\}_{j=1}^{M}$,   where   $(x,   x')_{j}$  is
  sentence  pair  grouped  by  2  user  input  queries and $l_{j}\in\{0, 1\}$ is
  similarity class label, see Equ. \ref{eq:similarity label},
  \begin{align}
    l_{j}=
    \begin{cases} \label{eq:similarity label}
      0 & y_{x}\neq y_{x'}\\
      1 & y_{x}=y_{x'}
    \end{cases}
  \end{align}
  directly  from  original data set $\mathcal{D}$ without any sampling strategy,
  then  $\mathcal{D'}$  will  have  $M=N^2$ data points of sentence pairs, which
  might be too time-consuming for the training process of stage 2 since we often
  have  hundreds  of class labels under task-specific chatbot scenario. Although
  we  may  only  have  a  few data points for a single class label, $M$ is still
  quite a big number.

@@

  After  explaining the data sampling principle for sentence pairs and how the 2
  stages  in  SFC  system  connect  with  each other, let's go deeper into model
  structure within these two stages respectively to see how it works.

@@

  Therefore,  the  overall  loss  function for multi-task learning in stage 2 is
  shown in Equ. \ref{eq: two-stage SFC loss}. The training objective of stage 2 is
  to  minimize  the  weighted  sum  of task-specific losses. Here $\alpha_S$ and
  $\alpha_K$  are  weights  of  task  1  and  task  2  respectively,  which  are
  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting.

  \begin{align}
    \mathcal{L} = \alpha_S \mathcal{L}^S + \alpha_K \mathcal{L}^K
    \label{eq: two-stage SFC loss}
  \end{align}

@@

  \subsection{joint SFC with joint model structure}
  Despite  the  outstanding experimental result of two-stage SFC on various tasks,
  we still find a limitation brought by the two-stage system structure. In two-stage
  SFC, Stage 1 and stage 2 are separate, so they do not interact with each other
  during  training.  In  this  case,  the  performance  of stage 1 can limit the
  potential  of  stage  2, meanwhile, stage 2 also cannot give training feedback
  back to stage 1 for fine-tuning.

  Therefore,  to  further  improve the overall performance of SFC, we proposed a
  joint  model  structure,  shown  in Fig. \ref{fig:framework}. In
  joint SFC, classification model is being placed in lower layer level to
  dynamically  provide  top-K  candidate  class  labels  for  the  sentence-pair
  similarity  model  placed in higher layer level through a top-K pooling layer.
  In  this way, classification model and similarity model can be merged into one
  single  joint-model  for  multi-task training with sentence pairs sampled from
  varying  candidate  class  labels,  thus  avoiding the limitation brought by 2
  separate stage structure.

  There  are  3  tasks in total during the training process of joint SFC,
  shown  in  Fig. \ref{fig:framework}, and the overall loss is also the weighted
  sum  of  all  the task-specific losses, shown in Equ. \ref{eq: hierachical SFC
  loss}. Here, $\alpha_S$, $\alpha_K$ and $\alpha_C$ are the weights for task 1:
  sentence-pair  similarity,  task  2:  top-K classification and task 3: general
  single   sentence  classification  respectively,  which  are  $\alpha_S=0.25$,
  $\alpha_K=0.25$ and $\alpha_C=0.5$ in our setting.

@@

          two-stage SFC & \multirow{2}*{$0.8979$} & \multirow{2}*{$0.9457$} & \multirow{2}*{$0.9517$} & \multirow{2}*{$0.7975$} & \multirow{2}*{$0.8818$} & \multirow{2}*{$0.8962$} & \multirow{2}*{$0.9109$} & \multirow{2}*{$0.6477$} & \multirow{2}*{$0.7055$} & \multirow{2}*{$0.7200$} & \multirow{2}*{$0.7232$} & \multirow{2}*{$0.7972$} & \multirow{2}*{$0.7189$}\tabularnewline

@@

          two-stage SFC & \multirow{2}*{$0.9162$} & \multirow{2}*{$0.9424$} & \multirow{2}*{$0.9530$} & \multirow{2}*{$0.7997$} & \multirow{2}*{$0.8823$} & \multirow{2}*{$0.8945$} & \multirow{2}*{$0.9123$} & \multirow{2}*{$0.6498$} & \multirow{2}*{$0.6980$} & \multirow{2}*{$0.7202$} & \multirow{2}*{$0.7358$} & \multirow{2}*{$0.8020$} & \multirow{2}*{$0.7311$}\tabularnewline

@@

          two-stage SFC & \multirow{2}*{$0.9167$} & \multirow{2}*{$0.9456$} & \multirow{2}*{$0.9571$} & \multirow{2}*{$0.7954$} & \multirow{2}*{$0.8854$} & \multirow{2}*{$0.8931$} & \multirow{2}*{$0.9192$} & \multirow{2}*{$0.6525$} & \multirow{2}*{$0.7001$} & \multirow{2}*{$0.7168$} & \multirow{2}*{$0.7476$} & \multirow{2}*{$\textbf{0.8124}$} & \multirow{2}*{$0.7364$}\tabularnewline

@@

          \multirow{2}*{joint SFC} & \multirow{2}*{$\textbf{0.9231}$} & \multirow{2}*{$\textbf{0.9560}$} & \multirow{2}*{$\textbf{0.9644}$} & \multirow{2}*{$\textbf{0.8270}$} & \multirow{2}*{$\textbf{0.9069}$} & \multirow{2}*{$\textbf{0.9103}$} & \multirow{2}*{$\textbf{0.9209}$} & \multirow{2}*{$\textbf{0.6697}$} & \multirow{2}*{$\textbf{0.7211}$} & \multirow{2}*{$\textbf{0.7254}$} & \multirow{2}*{$\textbf{0.7497}$} & \multirow{2}*{$0.8114$} & \multirow{2}*{$\textbf{0.7445}$}\tabularnewline

@@

  \textbf{Group  3:  SFC  system with ablation study.} This group of baseline is
  based  on  the network structure of two-stage SFC shown in \ref{fig:ver.1.3}. We
  conduct  ablation study by introducing single task SFC system with only Task 1
  or  Task  2  to  investigate  the influence of each component within the total
  loss.

@@

      \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline 
        \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
        \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7882$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7826$\tabularnewline
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
        \hline
      \end{tabular}
      \par
    \end{centering}
    \caption{
      We  show the performance of SFC from different settings of hyperparameters
      for  $K$,  the candidate class number, and $P$, the sample number for each
      class.
    }

@@

  \textbf{Comparison  among  SFC  variants.} First, we turn to compare among the
  four  SFC  variants shown in Table \ref{tbe:table2} to analyze the improvement
  brought  by  multi-task  and  joint-model  structure. We conduct
  ablation  experiments  to study the benefits brought by multi-task training by
  comparing multi-task two-stage SFC with single-task two-stage SFC. We can see from
  Table  \ref{tbe:table2}  that  two-stage  SFC  with  only  task 1 (sentence-pair
  similarity task) degrades by 0.65 percent on average and two-stage SFC with only
  task  2  (top-K  classification  task) degrades by 0.3 percent on average. The
  degradation  indicates  that  training  with these 2 tasks together in SFC can
  effectively  help  the  sentence-pair  model  extract  more knowledge from the
  limited  amount  of data. Besides, task 2 degrades 0.35 percent less than task
  1.  This observation suggests that task 2 may play a relatively more important
  role  in multi-task learning, which leads us to put larger weight $\alpha_{K}$
  to  the  loss  $\mathcal{L}^{K}$  of  task  2  when calculating the total loss
  $\mathcal{L}$.  Also, we can see that the hierachical SFC steadily outperforms
  two-stage  SFC  on  5  diverse  datasets  by  1.17  percents  on  average.  This
  observation  supports  the idea that the hierachical joint model structure can
  alleviate the limitation brought by the lack of interaction between similarity
  model  and  classification  model in two-stage SFC. Therefore, for the following
  analysis,  we  will  focus  on  the comparison between hierachical SFC and the
  other baseline models.

  \textbf{Analysis  under  few-shot  scenarios.}  Next,  we  analyze the overall
  improvement trend of SFC under various few-shot settings. Our main focus is to
  study chatbot building in common situation during real-world application where
  only  a  few  sample  sentences are available for each class. The experimental
  results  for  the  3  diverse  intent detection datasets (ClINC150, BANKING77,
  HWU64) under few-shot settings indicate that our proposed joint SFC can
  achieve  2.47  percents  average  improvement  over  one  of the most powerful
  baseline  models,  which  is  RoBERTa-large classification model, on all these
  few-shot  settings. Moreover, the improvement in F-score becomes more and more
  prominent  with the decrease of data sample number per class. Our joint
  SFC   can  achieve  4.97  percents  average  improvements  over  RoBERTa-large
  classification model in the most extreme few-shot setting with only 5 training
  samples  per class. This observation indicates that SFC is especially suitable
  for  being  applied during the initial stage of building task-specific chatbot
  system,  where  the  amount  of  data sample for each class label is extremely
  scarce.

  \textbf{Comparison  between  label  embedding  and  sentence  pair embedding.}
  Afterwards,  we  start  to  compare the performance of SFC with the text-label
  joint  embedding  baseline  named as LEAM. As shown in Table \ref{tbe:table2},
  joint  SFC outperforms LEAM by 14.25 percents on average F-score over 5
  datasets.  Besides,  although the labels within the 3 diverse intent detection
  datasets  (CLINC150,  BANKING77,  HWU64)  are  all  being  well-defined as the
  semantic  summary  of  each intent, joint SFC still outperforms LEAM by
  14.69  percents  on  average  F-score.  This  observation  indicates that it's
  usually  quite  hard  to  use  a  fixed  label  with  only  a few words as the
  representative  of  all  the  sentences  within a class since there are always
  plenty of ways for people to express questions or queries about the same topic
  during   a   conversation  with  chatbot.  Therefore,  learning  the  semantic
  similarity  between  user  query  and  sample  sentences through sentence pair
  embedding  can be more reliable than making decision according to the semantic
  relationship between user query and class labels through label embedding.

  \textbf{Fusion  of  classification  and  similarity  model.} Then, we begin to
  compare  the  general  performance  of SFC with single-task classification and
  similarity  baselines.  As  for  the  classification  model,  joint SFC
  outperforms    TextCNN    by   26.19   percents,   ALBERT-xxlarge   by   17.87
  percents\footnote{We found that the performance of ALBERT.xxlarge is extremely
  unstable  for  classification  task.  Here, we did multiple run with different
  settings  of parameters such as learning rate and batch size for each dataset,
  and  record  the  best  result  we  can  obtain  in  Table \ref{tbe:table2}.},
  BERT-large  by  9.81 percents, RoBERTa-base by 4.52 percents, RoBERTa-large by
  2.47 percents on average F-score over 5 datasets. In this way, we can see that
  RoBERTa  is  the  best  baseline  pre-trained  model for the low-resource text
  classification  task  we  are  studying.  As for the similarity model, we only
  choose  the  strongest  pretrained  model  RoBERTa-large  as our baseline, and
  joint  SFC  achieves  the  improvement  of  7.81  percents  on average.
  Moreover,  joint  SFC's  result on 2 datasets without data sampling for
  few-shot  settings,  which  are  ITG  and  Amazon-670k, are also 1.24 and 2.89
  percents  higher  than  Roberta-large  classification  model, and are 6.96 and
  10.77  percents higher than Roberta-large similarity model. These improvements
  illustrate that putting classification model and similarity model at different
  network  layers  to  cooperate  with  each  other  is  a  successful design of
  joint network structure for joint model, which enables these two models
  assist each other for better overall results.
